Uncovering Distributed System Bugs\\ during Testing (not Production!) -- draft title

### 2015-08-16 background.tex
added a reference to AWS using TLA+
added some of the quotes from Cheng regarding top problems

@@

>>>>

\subsection{Finding bugs in distributed systems}
\label{bg:bugs}

Draft -- We asked engineers in the Microsoft Azure team to tell us their number one problem when developing distributed systems. We got the following answers: ``Due to limited testing coverage, many correctness problems are only exposed in production through live-sites''; ``Engineering overhead extremely high to identify problems''; ``Practical tools that can improve testing coverage highly appreciated!''.

@@

%The \psharp language belongs to the same family of languages as P~\cite{desai2013p}.
